Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
Added citation for numeric representation, also clarified DSP

Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t), u_k$, respectively. 
Feedback architectures can be employed to manipulate the properties and behaviors of the continuous process (the plant).   
%reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. 
We are interested in the synthesis of digital feedback control algorithm, 
as implemented on modern FPGAs or DSPs. 
The most basic feedback architecture is the state feedback, 
where the control action $u_k$ (notice we work with the discretized signal) is computed by: 
%
\begin{equation}
\label{eq:controlaction}
u_k = r_{k} - K x_k. 
\end{equation}
%
Here $K \in \mathbb{R}^{m \times n}$ is a state feedback gain matrix, 
and $r_{k}$ is a reference signal (again digital).   
%
The closed-loop model then takes the form 
\begin{align}
\label{eq:closedloopss}
x_{k+1} = ( A_d - B_d K ) x_k + B_d r_k.
\end{align}
The gain matrix $K$ can be set so that the closed-loop discrete dynamics are shaped as desired, 
for instance according to a specific stability goal or around a specific dynamical behavior \cite{astrom1997computer}. 
As argued later in this work, we will target more complex objectives, such as quantitative safety requirements that are not typical in the digital control literature. 
Further, we will encompass the digital nature of the controller, which manipulates quantities with finite precision.

@@

The models we consider have two sources of error due to numeric representation. 
The first is the numeric error introduced by the fixed-point numbers employed to model the plant, i.e., to represent the plant dynamics $A_d$, $B_d$ and its states. 
The second is the quantization error introduced by the digital controller, 
which performs operations in the domain of fixed-point numbers. 
In this section we formally outline the errors introduced by the fixed-point representation of numbers. 
% 
Let $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$ represented in a fixed point domain, with $I$ bits representing the integer part and $F$ bits representing the decimal part. The smallest number that can be represented in this domain is $c_m=2^{-F}$.

>>>>

Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t), u_k$, respectively. 
Feedback architectures can be employed to manipulate the properties and behaviors of the continuous process (the plant).   
%reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. 
We are interested in the synthesis of digital feedback control algorithm, 
as implemented on modern FPGAs or Digital Signal Processorss. 
The most basic feedback architecture is the state feedback, 
where the control action $u_k$ (notice we work with the discretized signal) is computed by: 
%
\begin{equation}
\label{eq:controlaction}
u_k = r_{k} - K x_k. 
\end{equation}
%
Here $K \in \mathbb{R}^{m \times n}$ is a state feedback gain matrix, 
and $r_{k}$ is a reference signal (again digital).   
%
The closed-loop model then takes the form 
\begin{align}
\label{eq:closedloopss}
x_{k+1} = ( A_d - B_d K ) x_k + B_d r_k.
\end{align}
The gain matrix $K$ can be set so that the closed-loop discrete dynamics are shaped as desired, 
for instance according to a specific stability goal or around a specific dynamical behavior \cite{astrom1997computer}. 
As argued later in this work, we will target more complex objectives, such as quantitative safety requirements that are not typical in the digital control literature. 
Further, we will encompass the digital nature of the controller, which manipulates quantities with finite precision.

@@

The models we consider have two sources of error due to numeric representation. 
The first is the numeric error introduced by the fixed-point numbers employed to model the plant, i.e., to represent the plant dynamics $A_d$, $B_d$ and its states. 
The second is the quantization error introduced by the digital controller, 
which performs operations in the domain of fixed-point numbers. 
In this section we formally outline the errors introduced by the fixed-point representation of numbers~\cite{DBLP:conf/arith/BrainTRW15}. 
% 
Let $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$ represented in a fixed point domain, with $I$ bits representing the integer part and $F$ bits representing the decimal part. The smallest number that can be represented in this domain is $c_m=2^{-F}$.
